\documentclass[a4paper,10pt]{article}

\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}

\usepackage{fontawesome}
\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[colorlinks,pdftex]{hyperref}
\usepackage{fancyhdr}
\usepackage{multicol}
\usepackage{eurosym}
\usepackage{xcolor}
\usepackage{xfrac}
\usepackage{vwcol} 
\usepackage{adjustbox}
\usepackage{longtable}
\usepackage{array}
\usepackage[french]{babel}
\definecolor{myBlue}{rgb}{0,0,0.55}


\hypersetup{
    urlcolor = {[rgb]{0,0,0}}
}

\newcommand\dunderline[3][-1pt]{{\%
  \sbox0{#3}% 
  \ooalign{\copy0\cr\rule[\dimexpr#1-#2\relax]{\wd0}{#2}}}}

\pagestyle{fancy}
\fancyhf{} 
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\usepackage{geometry}
\geometry{top=0.2cm, bottom=0.4cm, left=0.3cm, right=0.3cm}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

%==== Spacing Variables ====
\newlength{\spaceSectionTitle}\setlength{\spaceSectionTitle}{-1pt}
\newlength{\spaceSectionRule}\setlength{\spaceSectionRule}{-5pt}
\newlength{\spaceItemEnd}\setlength{\spaceItemEnd}{-0.8pt}
\newlength{\spaceJobV}\setlength{\spaceJobV}{2pt}
\newlength{\spaceJobTech}\setlength{\spaceJobTech}{2pt}
\newlength{\spaceSubItem}\setlength{\spaceSubItem}{-4pt}
\newlength{\spaceItemListEnd}\setlength{\spaceItemListEnd}{-2pt}
\newlength{\spaceProjectList}\setlength{\spaceProjectList}{3pt}
\newlength{\spaceJobMission}\setlength{\spaceJobMission}{3pt}
\newlength{\spaceExpSection}\setlength{\spaceExpSection}{1pt}
\newlength{\spaceSecSep}\setlength{\spaceSecSep}{-3mm}
\newlength{\spaceEduSec}\setlength{\spaceEduSec}{-4mm}
\newlength{\spaceProjSec}\setlength{\spaceProjSec}{0.5mm}

% Sections formatting
\titleformat{\section}{
  \vspace{\spaceSectionTitle}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule\vspace{\spaceSectionRule}]
\renewcommand{\labelitemi}{\textbullet}

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{: #2\vspace{\spaceItemEnd}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{3pt}
  \small
  \item
    \begin{tabular*}{0.97\textwidth}[t]{l @{\extracolsep{\fill}}r}
      \normalsize{\textbf{#1}} & #4 \\
      \normalsize{\textit{#3}} & #2 \\
    \end{tabular*}
}

\def\Plus{\texttt{+\space}}

% -------- ORIGINAL ------------

\newcommand{\resumeSubItem}[2]{
    \small{\resumeItem{#1}{#2}\vspace{\spaceSubItem}}
	
}


\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*,label=\textbullet]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{\spaceItemListEnd}}


\newcommand{\resumeProjectListStart}{\begin{minipage}{0.97\textwidth} 
                                     \begin{itemize}[leftmargin=5mm]
                                     \vspace{\spaceProjectList}}
\newcommand{\resumeProjectListEnd}{\end{itemize} 
                                   \end{minipage}}
\newcommand{\resumeProjectItem}[1]{
    \item\small{#1}
    }

% New commands for detailed version
\newcommand{\resumeDetailedProject}[5]{
    \item\small{
        \textbf{#1} \hfill \textit{#2} \\ 
        \begin{minipage}{0.95\textwidth}
            \small{\textbf{Langages :} #3 \\ 
            \textbf{Outils/Packages :} #4 \\ 
            \textbf{Difficultés :} #5}
        \end{minipage}
    }
    \vspace{\spaceProjectList}
}

% New commands for consolidated job display
\newcommand{\resumeJobTechnologies}[1]{
    \vspace{\spaceJobTech}
    \small{\textbf{Technologies :} #1}\vspace{\spaceJobTech}
}

\newcommand{\resumeJobMission}[2]{
    \item\small{
        \textbf{#1} \\ 
        \begin{minipage}{0.95\textwidth}
            \small{#2}
        \end{minipage}
    }
    \vspace{\spaceJobMission}
}

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}


%----------HEADING-----------------
\begin{center}
  \begin{minipage}{0.97\textwidth}
      \begin{minipage}[c]{0.6\linewidth}
          \huge \textbf{Ulysse \textsc{Boucherie}}
          \\
          \emph{\large{DevOps Engineer \& Data Scientist (MSc.)}}
      \end{minipage}
      \hfill
      \begin{minipage}[c]{0.215\linewidth}
          \begin{tabular*}{\textwidth}{c@{\extracolsep{\fill}} l}
              \href{mailto:uboucherie1@gmail.com}{\raisebox{-0.055\height}{\faEnvelope}} & \href{mailto:uboucherie1@gmail.com}{\small{uboucherie1@gmail.com}} \\ 
              \href{https://github.com/odysseu}{\raisebox{-0.035\height}{\faGlobe}} & \href{https://odysseu.github.io/}{\small{odysseu.github.io}} \\ 
              \href{https://github.com/odysseu}{\raisebox{-0.035\height}{\faGithub}} & \href{https://github.com/odysseu}{\small{odysseu}} \\ 
              \href{https://www.linkedin.com/in/ulysse-boucherie-7a3b2b111/}{\raisebox{-0.0925\height}{\faLinkedinSquare}} & \href{https://www.linkedin.com/in/ulysse-boucherie-7a3b2b111/}{\small{in/ulysse.boucherie}} \\ 
              {\raisebox{-0.0925\height}{\faHome}} & \small{Fontainebleau, France}
          \end{tabular*}
      \end{minipage}
  \end{minipage}
  \end{center}


%------------PROJET-----------------------

% \begin{center}
% \begin{minipage}{0.5\textwidth}
%     \centering
%     \large \textbf{Ingénieur DevOps \& data au service de la modernisation des Services Statistiques Publics}
% \end{minipage}
% \end{center}

% \vspace{\spaceSecSep}

%-----------EXPERIENCE-----------------
\section{Experience}

\resumeSubHeadingListStart

% \vspace{\spaceExpSection}

\resumeSubheading{\href{https://www.interieur.gouv.fr/Interstats/Actualites}{Ministry of the Interior}}{Paris, France}{Data Scientist and IT Technical Lead}{2024 - today}

\resumeProjectListStart
\resumeJobMission{Data engineering (DuckDB, PostgreSQL)}{Redesigned ETL processes for 20\Plus agents, reducing delays by over 80\%. Team training on processes and tools.}
\resumeJobMission{LLM models for reformulating and clustering survey responses (Python, HuggingFace)}{Co-design, build and run of LLM models for clustering responses to validate other fields.}
\resumeJobMission{Head of economic and financial crime studies (Quarto, VS Code, Markdown, R, RStudio, CI/CD)}{Analysis and visualization model pipelines using Police Nationale and Gendarmerie data.}
\resumeJobMission{Culture change initiative (Git, Microsoft and Libre Office suites, Peer Programming)}{ Modernization of practices. More standard tools and working methods. Documentation, tutorials, workshop facilitation.}
\resumeJobMission{Initiative for the development of open-source publication tools (Quarto, Markdown, Notebook, GitHub)}{Industrialized publication of articles and public content, reducing technical debt and costly proprietary dependencies.}
\resumeProjectListEnd

\resumeSubheading{\href{https://www.insee.fr/fr/accueil}{INSEE}}{Nantes, France}{DevOps Engineer Data Plateform}{2021 -- 2024}
\resumeProjectListStart
\resumeJobMission{Platform Engineer (Go, Kubernetes, Helm, Docker, Podman, GitLab CI/CD, GitHub Actions, ArgoCD, Vault, Prometheus, Grafana, ELK, OpenTelemetry, Terraform, S3)}{Product mode, \textit{build} and Administration of the K8s cluster and the containerized \textit{Platform As A Service} (\href{https://github.com/InseeFrLab/onyxia}{\textit{Onyxia}}).}
\resumeJobMission{Modernization of the old data science platform (TypeScript)}{Migration of Windows Server services to K8s, process automation, reduction of \textit{time to market} and technical debt.}
\resumeJobMission{Support for Data Scientists (Jupyter Notebook, RStudio Server, PyCharm, VS Code)}{Incident resolution, integration of production Data Science and Machine Learning services.}
\resumeProjectListEnd


\resumeSubheading{\href{https://www.insee.fr/fr/accueil}{INSEE}}{Nantes, France}{Data plateform Engineer}{2020 -- 2021}
\resumeProjectListStart
\resumeJobMission{System administration of the data science platform (VMware, AGDLP, OIDC, LDAP, Puppet, Ansible)}{Build and Run of components for 500\Plus data scientists daily, saving 80\% time on shared self-service services.}
\resumeJobMission{Build and Run of a resource monitoring system (PowerShell, TaskManager, Active Directory)}{Supervision and planning of shared physical resource allocation, SMTP alerting, recovery of 20\Plus of used resources.}
\resumeJobMission{Migration from proprietary language used for 20\Plus years to open source (SAS)}{Translation of production project code. \textit{Blue-green} and \textit{canary} methods. Development of migration tools.}
\resumeProjectListEnd

\resumeSubheading{\href{https://www.cso.ie}{Central Statistics Office}}{Dublin, Ireland}{End-of-studies Internship}{Summer 2020}
\resumeProjectListStart
\resumeJobMission{Machine learning on meteorological data}{Specifications and POC of the OCR pipeline for automatic reading of 250\Plus years of monthly manual records.}
\resumeJobMission{Statistical Assistant}{Ireland's official annual reports. Parameterized pipeline for report generation.}
\resumeProjectListEnd

\resumeSubHeadingListEnd

%-----------COMPETENCES TECHNIQUES + LANGUES -----------------
\begin{minipage}[t]{0.75\linewidth}
    %-----------EDUCATION-----------------
    \section{Education}
    \resumeSubHeadingListStart
    \vspace{\spaceExpSection}
    
    \resumeSubheading{ENSAI}{Rennes, France}{Engineering Degree (MSc.)}{2018 -- 2021}
    \resumeProjectListStart
    \resumeProjectItem{Computer Science specialization, Class delegate, Vice president of the Sports Office}
    \resumeProjectListEnd
    
    \resumeSubheading{\textit{Lycée International François Premier}}{Fontainebleau, France}{Classe Préparatoire aux Grandes écoles}{2015 -- 2018}
    \resumeProjectListStart
    \resumeProjectItem{\textit{MPSI -- MP}: Engineering Sciences, Computer Science specialization, Class delegate}
    \resumeProjectListEnd
    
    \resumeSubheading{Rim of the World High School}{Lake Arrowhead, California, USA}{Full immersion school year}{2011- 2012}
    
    \resumeSubHeadingListEnd
    
\end{minipage}
\hfill
\begin{minipage}[t]{0.2\linewidth}
    \section{Languages}
    \resumeSubHeadingListStart
    \resumeSubItem{French}{Native}
    \resumeSubItem{English}{Fluent}
    \resumeSubItem{Spanish}{Intermediate}
    \resumeSubHeadingListEnd
\end{minipage}


%\vspace{\spaceProjSec}

%-----------PROJECTS-----------------
\section{Personal Projects and Interests}
\vspace{\spaceProjSec}
\begin{minipage}[t]{0.9865\textwidth}

\resumeSubHeadingListStart
    \resumeSubItem{Real Estate Web Application}{Optimization between renting and buying a property with real parameters: \href{https://odysseu.github.io/HabitatCalc/}{\textit{HabitatCalc}}.}
    \resumeSubItem{Tax Web Application}{Understanding marginal tax brackets on income and tax rates: \href{https://odysseu.github.io/TrancheMaster/}{\textit{TrancheMaster}}.}
    \resumeSubItem{Mobile Game Dashboard}{Dashboard of real data from a mobile role-playing game: \href{https://github.com/odysseu/Brawlstar-Club-Dashboard.github.io}{\textit{BrawlStar Club Dashboard}}.}
    \resumeSubItem{Open Source Contributions}{\href{https://github.com/quarto-dev/quarto-cli}{\textit{Quarto cli}}, \href{https://github.com/InseeFrLab/onyxia}{\textit{Onyxia}}, Python, R and JavaScript packages}
    \resumeSubItem{Conferences and Seminars}{\href{https://www.numerique.gouv.fr/agenda/etat-dans-le-nuage-2026/}{\textit{The State in the Cloud 2026}}, INSEE and Public Statistical Services Webinars 2024 to 2026, AI Salon 2023, KubeCon 2023, DevFest 2022 \& 2023, VivaTech 2022}
    \resumeSubItem{Sports}{Triathlon, volleyball, beach volleyball, alpine skiing, bouldering}
    \resumeSubItem{Music}{Piano (4 years), drums (10 years)}
\resumeSubHeadingListEnd
\end{minipage}

%-------------------------------------------
\end{document}
